BIP Architectures and Open pNets

### 2019-01-18 2018-Arch-pNets/arch-pNets.tex
arch-pNets: (Minor) Separated timeout port in Timer and Ctrl into timeout_T and timeout_C
Eric: nouveau listing pour les OTs du FailureTimer

The model in \fig{schema:ArchFailure:BIP} has two components:
%% The
%% component $\NameOprnd$ is an \emph{operand} of the architecture, \ie
%% it only has its interface defined: $(\emptyset, \{\PortFinish,
%% \PortResume, \PortFail\}, \export[\emptyset])$, with
%% $\export[\emptyset](p) = \emptyset$, for all $p \in \{\PortFinish,
%% \PortResume, \PortFail\}$.  
%% The other two components,
%
$\NameTimer$ and $\NameCtrl$, with interfaces
\[\bigl(
\{t, z\},
\{\PortTick, \PortCancel, \PortTO\},
\export[\NameTimer]
\bigr)\,,
\qquad
\export[\NameTimer](p) =
\begin{cases}
  \{t, z\}, & \text{if } p = \PortTick,\\
  \emptyset, & \text{otherwise}
\end{cases}
\]
and
\[\bigl(
\{\mathit{zone}\},
\{\PortReset, \PortFail, \PortResume, \PortTO\},
\export[\NameCtrl]
\bigr)\,,
\quad
\export[\NameCtrl](p) =
\begin{cases}
  \{\mathit{zone}\}, & \text{if } p = \PortFail,\\
  \emptyset, & \text{otherwise}
\end{cases}
\]
%
respectively. %% , where $\export[\NameCtrl](\PortFail) =
%% \{\mathit{zone}\}$ and $\export[\NameCtrl](p) = \emptyset$, for all
%% other ports $p$; $\export[\NameTimer](\PortTick) = \{t, z\}$ and
%% $\export[\NameTimer](p) = \emptyset$, for all other ports $p$.
Variable $t$ is implicitly assumed to be an integer.  Variables $z$
and $\mathit{zone}$ are implicitly assumed to be integer intervals of
the form $[l,u]$.  For both types, we also implicitly assume the
natural ordering: increasing integers and interval inclusion.

@@

\begin{example}
  The architecture in \fig{schema:ArchFailure:BIP} enforces the
  following properties:
  \begin{enumerate}
  \item There is always a possibility to reset the system after a
    failure:
    \begin{equation}
      \label{eq:prop:reset:can}
      \AG (\PortFail \rightarrow \EF \PortReset).
    \end{equation}
  \item Whenever a reset is requested, it will eventually be
    effectuated:
    \begin{equation}
      \label{eq:prop:reset:will}
      \AG (\PortAsk \rightarrow \AF \PortReset).
    \end{equation}
  \item As long as no failure has occured, the $z$ variable of the
    $\NameTimer$ component has the value $\topinterval$:
    \begin{equation}
      \label{eq:prop:z:top}
      \AW[\quad]{(z = T)}{\PortFail} \land\quad
      \AG \bigl(
      \PortReset \rightarrow \AW[]{(z = T)}{\PortFail}
      \bigr).
    \end{equation}
  \item A timeout can only occur within the specified delay after
    a failure:
    \begin{multline}
      \label{eq:prop:to:delay}
      \forall T_0, T_1 \in \sZ,\
      \AG \Big((\PortFail \land \NameTimer.t = T_0) \rightarrow
      \\
      \AW[]{\bigl((\PortTO \land \NameTimer.t = T_1) \rightarrow
        (T_1 - T_0 \in \NameCtrl.\mathit{zone})\bigr)
      }{
        (\PortReset \lor \PortResume)
      }\Big),
    \end{multline}
    where $T_0$ and $T_1$ are integer parameters.  (The formula
    holds with the universal quantification over $T_0$ and $T_1$
    due to the fact that their individual values only appear in
    the left-hand sides of the two implications.)
  \end{enumerate}
\end{example}

@@

      \node[node distance=1cm] (ab) [below of=start] {\NameTimer.\PortTO};
      \node[node distance=2.1cm] (ac) [right of=ab]{\NameCtrl.\PortTO};
      \node[node distance=1.5cm] (aa) [left of=ab]{\PortAsk};

      \draw [style=-*, thick, black] ($(h4.south)+(0,.1cm)$) -- ++(right:.5cm) -| (ac.north);
      \draw [style=-*, thick, black]  ($(h4.south)+(0,.1cm)$) -| (ab.north);
      \draw [style=-*, thick, black]  ($(h4.south)+(0,.1cm)$) -| (aa.north);
    \end{tikzpicture}
%
    &
%
    \begin{tikzpicture}[shorten >=1pt,node distance=.7cm,>=stealth']
      \node (start) {\color{red}\PortAsk\ \NameTimer.\PortTO\ \NameCtrl.\PortTO};
      \node()[below of=start]{};
    \end{tikzpicture}
%
    &
%
    $
    \begin{array}[b]{c@{}}
      {\color{red}
        \begin{aligned}
          \NameCtrl.\PortTO &\Rightarrow
          \PortAsk \land \NameTimer.\PortTO
          \\
          \NameTimer.\PortTO &\Rightarrow 
          \PortAsk \land \NameCtrl.\PortTO
        \end{aligned}}
      \\[11pt]
      {\color{red}
        \begin{aligned}
          \PortAsk &\Rightarrow
          \NameTimer.\PortTO \land \NameCtrl.\PortTO
          \\
          \true &\Rightarrow
          \PortAsk \land \NameTimer.\PortTO
          \land \NameCtrl.\PortTO
        \end{aligned}

@@

-------------------------------------------
INFO  BIPArchFailureTimerMax_LTF3 - Total: 12 OTs
INFO  BIPArchFailureTimerMax_LTF3 -
        {t0---init-->t1, s0---init-->s1},   {},   
        [((init=:ra:117:1))/\((:ra:117:1=init))/\((init=:ra:118:1))/\((:ra:118:1=init))
          /\((alpha4=:ra:1:5))],   {t := 0, z := TopInt, zone := minZone,maxZone}
    OT1 ------------------------------------------------------------
        <t0_s0>-----:ra:1:5----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
     {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B:13:1-->},   
     [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
       /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
       /\((fail(zone, false)=:ra:12:1))
       /\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))/\
       ((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)/\
       (z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
       /\((alpha0=:ra:1:1))],
   {t := (t+1), z := z1}
    OT2 ------------------------------------------------------------
        <t1_s1>-----:ra:1:1----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B:13:1-->},
   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
     /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
     /\((fail(zone, true)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
     /\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)
     /\(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
     /\((alpha0=:ra:1:1))],   {t := (t+1), z := z1}
    OT3 ------------------------------------------------------------
        <t1_s1>-----:ra:1:1----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B:17:3-->},
   [((cancel(false)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
     /\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
    OT4 ------------------------------------------------------------
        <t1_s1>-----:ra:1:2----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
{t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E:112:6-->},
[(t in z)/\((timeout=:ra:19:1))/\((:ra:19:1=timeout))
/\((timeout=:ra:110:1))/\((:ra:110:1=timeout))/\((:hb_E:112:6=ask))/\((alpha2=:ra:1:3))], {t := (t+1)}
    OT5 ------------------------------------------------------------
        <t1_s1>-----:ra:1:3----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B:13:1-->},
   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
     /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
     /\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
     /\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)
     /\(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
     /\((alpha0=:ra:1:1))],   {t := (t+1), z := z1}
    OT6 ------------------------------------------------------------
        <t1_s2>-----:ra:1:1----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B:17:3-->},
   [((cancel(false)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
     /\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
    OT7 ------------------------------------------------------------
        <t1_s2>-----:ra:1:2----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B:17:3-->},
   [((cancel(true)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
     /\((resume(true)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],
   {t := 0, z := TopInt}
    OT8 ------------------------------------------------------------
        <t1_s2>-----:ra:1:2----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E:112:6-->},
   [(t in z)/\((timeout=:ra:19:1))/\((:ra:19:1=timeout))
     /\((timeout=:ra:110:1))/\((:ra:110:1=timeout))/\((:hb_E:112:6=ask))/\((alpha2=:ra:1:3))],
   {t := (t+1)}
    OT9 ------------------------------------------------------------
        <t1_s2>-----:ra:1:3----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B:13:1-->},
   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
     /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
     /\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
     /\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)
     /\(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
     /\((alpha0=:ra:1:1))],   {t := (t+1), z := z1}
    OT10 ------------------------------------------------------------
        <t1_s3>-----:ra:1:1----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B:17:3-->},
   [((cancel(false)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
     /\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
    OT11 ------------------------------------------------------------
        <t1_s3>-----:ra:1:2----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
   {s3---reset-->s1},   {---:hb_E:116:8-->},
   [((reset=:ra:114:1))/\((:ra:114:1=reset))/\((:hb_E:116:8=reset))/\((alpha3=:ra:1:4))],   {}
    OT12 ------------------------------------------------------------
        <t1_s3>-----:ra:1:4----><t1_s1>

>>>>

The model in \fig{schema:ArchFailure:BIP} has two components:
%% The
%% component $\NameOprnd$ is an \emph{operand} of the architecture, \ie
%% it only has its interface defined: $(\emptyset, \{\PortFinish,
%% \PortResume, \PortFail\}, \export[\emptyset])$, with
%% $\export[\emptyset](p) = \emptyset$, for all $p \in \{\PortFinish,
%% \PortResume, \PortFail\}$.  
%% The other two components,
%
$\NameTimer$ and $\NameCtrl$, with interfaces
\[\bigl(
\{t, z\},
\{\PortTick, \PortCancel, \PortTOT\},
\export[\NameTimer]
\bigr)\,,
\qquad
\export[\NameTimer](p) =
\begin{cases}
  \{t, z\}, & \text{if } p = \PortTick,\\
  \emptyset, & \text{otherwise}
\end{cases}
\]
and
\[\bigl(
\{\mathit{zone}\},
\{\PortReset, \PortFail, \PortResume, \PortTOC\},
\export[\NameCtrl]
\bigr)\,,
\quad
\export[\NameCtrl](p) =
\begin{cases}
  \{\mathit{zone}\}, & \text{if } p = \PortFail,\\
  \emptyset, & \text{otherwise}
\end{cases}
\]
%
respectively. %% , where $\export[\NameCtrl](\PortFail) =
%% \{\mathit{zone}\}$ and $\export[\NameCtrl](p) = \emptyset$, for all
%% other ports $p$; $\export[\NameTimer](\PortTick) = \{t, z\}$ and
%% $\export[\NameTimer](p) = \emptyset$, for all other ports $p$.
Variable $t$ is implicitly assumed to be an integer.  Variables $z$
and $\mathit{zone}$ are implicitly assumed to be integer intervals of
the form $[l,u]$.  For both types, we also implicitly assume the
natural ordering: increasing integers and interval inclusion.

@@

\begin{example}
  The architecture in \fig{schema:ArchFailure:BIP} enforces the
  following properties:
  \begin{enumerate}
  \item There is always a possibility to reset the system after a
    failure:
    \begin{equation}
      \label{eq:prop:reset:can}
      \AG (\PortFail \rightarrow \EF \PortReset).
    \end{equation}
  \item Whenever a reset is requested, it will eventually be
    effectuated:
    \begin{equation}
      \label{eq:prop:reset:will}
      \AG (\PortAsk \rightarrow \AF \PortReset).
    \end{equation}
  \item As long as no failure has occured, the $z$ variable of the
    $\NameTimer$ component has the value $\topinterval$:
    \begin{equation}
      \label{eq:prop:z:top}
      \AW[\quad]{(z = T)}{\PortFail} \land\quad
      \AG \bigl(
      \PortReset \rightarrow \AW[]{(z = T)}{\PortFail}
      \bigr).
    \end{equation}
  \item A timeout can only occur within the specified delay after
    a failure:
    \begin{multline}
      \label{eq:prop:to:delay}
      \forall T_0, T_1 \in \sZ,\
      \AG \Big((\PortFail \land \NameTimer.t = T_0) \rightarrow
      \\
      \AW[]{\bigl((\PortTOC \land \NameTimer.t = T_1) \rightarrow
        (T_1 - T_0 \in \NameCtrl.\mathit{zone})\bigr)
      }{
        (\PortReset \lor \PortResume)
      }\Big),
    \end{multline}
    where $T_0$ and $T_1$ are integer parameters.  (The formula
    holds with the universal quantification over $T_0$ and $T_1$
    due to the fact that their individual values only appear in
    the left-hand sides of the two implications.)
  \end{enumerate}
\end{example}

@@

      \node[node distance=1cm] (ab) [below of=start] {\NameTimer.\PortTOT};
      \node[node distance=2.1cm] (ac) [right of=ab]{\NameCtrl.\PortTOC};
      \node[node distance=1.5cm] (aa) [left of=ab]{\PortAsk};

      \draw [style=-*, thick, black] ($(h4.south)+(0,.1cm)$) -- ++(right:.5cm) -| (ac.north);
      \draw [style=-*, thick, black]  ($(h4.south)+(0,.1cm)$) -| (ab.north);
      \draw [style=-*, thick, black]  ($(h4.south)+(0,.1cm)$) -| (aa.north);
    \end{tikzpicture}
%
    &
%
    \begin{tikzpicture}[shorten >=1pt,node distance=.7cm,>=stealth']
      \node (start) {\color{red}\PortAsk\ \NameTimer.\PortTOT\ \NameCtrl.\PortTOC};
      \node()[below of=start]{};
    \end{tikzpicture}
%
    &
%
    $
    \begin{array}[b]{c@{}}
      {\color{red}
        \begin{aligned}
          \NameCtrl.\PortTOC &\Rightarrow
          \PortAsk \land \NameTimer.\PortTOT
          \\
          \NameTimer.\PortTOT &\Rightarrow 
          \PortAsk \land \NameCtrl.\PortTOC
        \end{aligned}}
      \\[11pt]
      {\color{red}
        \begin{aligned}
          \PortAsk &\Rightarrow
          \NameTimer.\PortTOT \land \NameCtrl.\PortTOC
          \\
          \true &\Rightarrow
          \PortAsk \land \NameTimer.\PortTOT
          \land \NameCtrl.\PortTOC
        \end{aligned}

@@

INFO  BIPArchFailureTimerMax_LTF3 -
       {t0---init-->t1, s0---init-->s1},   {},  [true],
       {t := 0, z := TopInt, zone := minZone,maxZone}
    OT1 ------------------------------------------------------------
        <t0_s0>-----alpha4----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT2 ------------------------------------------------------------
        <t1_s1>-----alpha0----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z,t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, true))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT3 ------------------------------------------------------------
        <t1_s1>-----alpha0----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)
         /\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))
         /\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT4 ------------------------------------------------------------
        <t1_s1>-----alpha1----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E-->},
       [(:hb_E=ask)/\(t in z)],   {t := t+1}
    OT5 ------------------------------------------------------------
        <t1_s1>-----alpha2----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT6 ------------------------------------------------------------
        <t1_s2>-----alpha0----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT7 ------------------------------------------------------------
        <t1_s2>-----alpha1----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(true))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(true))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],
       {t := 0, z := TopInt}
    OT8 ------------------------------------------------------------
        <t1_s2>-----alpha1----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E-->},
       [(:hb_E=ask)/\(t in z)],   {t := t+1}
    OT9 ------------------------------------------------------------
        <t1_s2>-----alpha2----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT10 ------------------------------------------------------------
        <t1_s3>-----alpha0----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT11 ------------------------------------------------------------
        <t1_s3>-----alpha1----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
        {s3---reset-->s1},   {---:hb_E-->},     [(:hb_E=ask)],   {}
    OT12 ------------------------------------------------------
        <t1_s3>-----alpha3----><t1_s1>
